Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-19 article.tex
precisie preprocessing
use subfigure

We will compare our approach to the Pearson correlation (see Section
\ref{sec:inference}), the generalized transfer entropy (GTE) and GENIE3.
\begin{itemize}
\item \textbf{GTE} \citep{stetter2012model}
, the baseline of the challenge, measures for all pairs of
neurons $i$ and $j$ the reduction of uncertainty in predicting future values of
$i$ given the observation of the time series of the neuron $j$
conditionally to the observation of past time series of neuron $i$,
whenever the average fluorescence is over a conditioning level.
Conditioning level was set to reproduce baseline of the challenge.
\textcolor{red}{Talk about pre-processing}

@@

\begin{figure}[bth]
\centering
\includegraphics[width=\linewidth]{images/curves}
\caption{Method precision-recall and ROC curves. \textcolor{red}{GENI3?}
         $\tau=0.11$}
\label{fig:curves}
\end{figure}

>>>>

We will compare our approach to the Pearson correlation (see Section
\ref{sec:inference}), the generalized transfer entropy (GTE) and GENIE3.
\begin{itemize}
\item \textbf{GTE} \citep{stetter2012model}
, the baseline of the challenge, measures for all pairs of
neurons $i$ and $j$ the reduction of uncertainty in predicting future values of
$i$ given the observation of the time series of the neuron $j$
conditionally to the observation of past time series of neuron $i$,
whenever the average fluorescence is over a conditioning level.
Pre-processing and conditioning level were set to reproduce baseline of the
challenge.

@@

\begin{figure}[bth]
\centering
\subfigure[]{\includegraphics[width=0.45\textwidth]{images/curve_roc} \label{fig:roc_curve}}
\subfigure[]{\includegraphics[width=0.45\textwidth]{images/curve_pr} \label{fig:pr_curve}}
\caption{Method precision-recall and ROC curves. \textcolor{red}{GENI3?}
         $\tau=0.11$}
\label{fig:curves}
\end{figure}
